### 2024-02-24 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: repesenting.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="repesenting_files/md-default6.js" type="text/javascript"></script><script src="repesenting_files/md-default7.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

# Representing ggplot plots as Clojure data

## Setup

We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.

::: {.sourceClojure}
```clojure
(ns repesenting
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.walk :as walk]
            [tablecloth.api :as tc]
            [editscript.core :as editscript]
            [clojure.pprint :as pp]
            [clojure.string :as str]))
```
:::

Loading ggplot2:

::: {.sourceClojure}
```clojure
(r/library "ggplot2")
```
:::

::: {.printedClojure}
```clojure
[1] "ggplot2"   "Rserve"    "stats"     "graphics"  "grDevices" "utils"    
[7] "datasets"  "methods"   "base"

Requireing the base R library as a Clojure namespace:

::: {.sourceClojure}
```clojure
(r/require-r '[base])
```
:::

::: {.printedClojure}
```clojure
nil

## An example plot

Here is how we may generate and display a plot:

::: {.sourceClojure}
```clojure
(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method=\"lm\")
         + facet_wrap(~cyl))"
    r
    plotting/plot->svg
    kind/html)
```
:::

```{=html}
<?xml version="1.0" encoding="UTF-8"?>
<svg xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink" width="504pt" height="504pt" viewBox="0 0 504 504" version="1.1">
<defs>
<g>
<symbol overflow="visible" id="glyph0-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph0-1">
<path style="stroke:none;" d="M 4.375 -4.703125 C 4.234375 -5.75 3.5625 -6.359375 2.609375 -6.359375 C 1.921875 -6.359375 1.3125 -6.03125 0.9375 -5.453125 C 0.546875 -4.828125 0.375 -4.0625 0.375 -2.90625 C 0.375 -1.828125 0.53125 -1.15625 0.90625 -0.59375 C 1.234375 -0.078125 1.78125 0.203125 2.46875 0.203125 C 3.65625 0.203125 4.515625 -0.6875 4.515625 -1.921875 C 4.515625 -3.09375 3.71875 -3.921875 2.609375 -3.921875 C 1.984375 -3.921875 1.5 -3.6875 1.171875 -3.234375 C 1.171875 -4.796875 1.671875 -5.671875 2.5625 -5.671875 C 3.109375 -5.671875 3.484375 -5.328125 3.609375 -4.703125 Z M 2.5 -3.234375 C 3.25 -3.234375 3.71875 -2.703125 3.71875 -1.859375 C 3.71875 -1.0625 3.1875 -0.484375 2.484375 -0.484375 C 1.765625 -0.484375 1.21875 -1.09375 1.21875 -1.90625 C 1.21875 -2.6875 1.734375 -3.234375 2.5 -3.234375 Z M 2.5 -3.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-2">
<path style="stroke:none;" d="M 3.4375 -3.359375 C 4.09375 -3.75 4.296875 -4.0625 4.296875 -4.65625 C 4.296875 -5.671875 3.53125 -6.359375 2.421875 -6.359375 C 1.3125 -6.359375 0.546875 -5.671875 0.546875 -4.671875 C 0.546875 -4.0625 0.75 -3.75 1.390625 -3.359375 C 0.671875 -2.984375 0.328125 -2.46875 0.328125 -1.765625 C 0.328125 -0.609375 1.171875 0.203125 2.421875 0.203125 C 3.65625 0.203125 4.515625 -0.609375 4.515625 -1.765625 C 4.515625 -2.46875 4.15625 -2.984375 3.4375 -3.359375 Z M 2.421875 -5.671875 C 3.078125 -5.671875 3.5 -5.28125 3.5 -4.640625 C 3.5 -4.046875 3.0625 -3.65625 2.421875 -3.65625 C 1.765625 -3.65625 1.34375 -4.046875 1.34375 -4.65625 C 1.34375 -5.28125 1.765625 -5.671875 2.421875 -5.671875 Z M 2.421875 -3 C 3.1875 -3 3.71875 -2.484375 3.71875 -1.75 C 3.71875 -0.984375 3.203125 -0.484375 2.40625 -0.484375 C 1.640625 -0.484375 1.125 -1 1.125 -1.734375 C 1.125 -2.5 1.640625 -3 2.421875 -3 Z M 2.421875 -3 "/>
</symbol>
<symbol overflow="visible" id="glyph0-3">
<path style="stroke:none;" d="M 2.875 -1.546875 L 2.875 0 L 3.65625 0 L 3.65625 -1.546875 L 4.578125 -1.546875 L 4.578125 -2.234375 L 3.65625 -2.234375 L 3.65625 -6.359375 L 3.078125 -6.359375 L 0.25 -2.359375 L 0.25 -1.546875 Z M 2.875 -2.234375 L 0.921875 -2.234375 L 2.875 -5.046875 Z M 2.875 -2.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-4">
<path style="stroke:none;" d="M 4.1875 -6.234375 L 0.96875 -6.234375 L 0.5 -2.84375 L 1.21875 -2.84375 C 1.578125 -3.265625 1.875 -3.421875 2.359375 -3.421875 C 3.203125 -3.421875 3.71875 -2.84375 3.71875 -1.921875 C 3.71875 -1.03125 3.203125 -0.484375 2.359375 -0.484375 C 1.6875 -0.484375 1.265625 -0.828125 1.078125 -1.53125 L 0.3125 -1.53125 C 0.40625 -1.015625 0.5 -0.78125 0.6875 -0.546875 C 1.03125 -0.078125 1.671875 0.203125 2.375 0.203125 C 3.640625 0.203125 4.515625 -0.71875 4.515625 -2.03125 C 4.515625 -3.265625 3.6875 -4.109375 2.5 -4.109375 C 2.0625 -4.109375 1.703125 -4 1.34375 -3.734375 L 1.59375 -5.46875 L 4.1875 -5.46875 Z M 4.1875 -6.234375 "/>
</symbol>
<symbol overflow="visible" id="glyph0-5">
<path style="stroke:none;" d="M 2.28125 -4.53125 L 2.28125 0 L 3.046875 0 L 3.046875 -6.359375 L 2.546875 -6.359375 C 2.265625 -5.390625 2.09375 -5.25 0.890625 -5.09375 L 0.890625 -4.53125 Z M 2.28125 -4.53125 "/>
</symbol>
<symbol overflow="visible" id="glyph0-6">
<path style="stroke:none;" d="M 2.421875 -6.359375 C 1.84375 -6.359375 1.3125 -6.09375 0.984375 -5.671875 C 0.578125 -5.109375 0.375 -4.25 0.375 -3.078125 C 0.375 -0.9375 1.078125 0.203125 2.421875 0.203125 C 3.734375 0.203125 4.453125 -0.9375 4.453125 -3.03125 C 4.453125 -4.25 4.265625 -5.078125 3.859375 -5.671875 C 3.53125 -6.109375 3.015625 -6.359375 2.421875 -6.359375 Z M 2.421875 -5.671875 C 3.25 -5.671875 3.671875 -4.828125 3.671875 -3.09375 C 3.671875 -1.28125 3.265625 -0.4375 2.40625 -0.4375 C 1.578125 -0.4375 1.171875 -1.3125 1.171875 -3.0625 C 1.171875 -4.828125 1.578125 -5.671875 2.421875 -5.671875 Z M 2.421875 -5.671875 "/>
</symbol>
<symbol overflow="visible" id="glyph0-7">
<path style="stroke:none;" d="M 4.453125 -0.765625 L 1.171875 -0.765625 C 1.25 -1.296875 1.53125 -1.625 2.296875 -2.09375 L 3.171875 -2.59375 C 4.046875 -3.0625 4.5 -3.71875 4.5 -4.5 C 4.5 -5.03125 4.28125 -5.53125 3.921875 -5.875 C 3.546875 -6.203125 3.09375 -6.359375 2.5 -6.359375 C 1.703125 -6.359375 1.125 -6.078125 0.78125 -5.53125 C 0.546875 -5.203125 0.453125 -4.796875 0.4375 -4.15625 L 1.21875 -4.15625 C 1.234375 -4.59375 1.296875 -4.84375 1.40625 -5.0625 C 1.59375 -5.4375 2 -5.6875 2.46875 -5.6875 C 3.171875 -5.6875 3.703125 -5.171875 3.703125 -4.484375 C 3.703125 -3.96875 3.40625 -3.53125 2.859375 -3.21875 L 2.046875 -2.75 C 0.75 -2 0.375 -1.40625 0.296875 -0.015625 L 4.453125 -0.015625 Z M 4.453125 -0.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph0-8">
<path style="stroke:none;" d="M 1.9375 -2.921875 L 2.359375 -2.921875 C 3.203125 -2.921875 3.65625 -2.53125 3.65625 -1.765625 C 3.65625 -0.96875 3.171875 -0.484375 2.375 -0.484375 C 1.515625 -0.484375 1.109375 -0.921875 1.0625 -1.84375 L 0.28125 -1.84375 C 0.3125 -1.34375 0.40625 -1 0.546875 -0.71875 C 0.875 -0.109375 1.484375 0.203125 2.34375 0.203125 C 3.625 0.203125 4.453125 -0.578125 4.453125 -1.78125 C 4.453125 -2.59375 4.140625 -3.03125 3.390625 -3.296875 C 3.96875 -3.53125 4.265625 -3.96875 4.265625 -4.609375 C 4.265625 -5.703125 3.546875 -6.359375 2.359375 -6.359375 C 1.109375 -6.359375 0.4375 -5.65625 0.40625 -4.3125 L 1.1875 -4.3125 C 1.203125 -4.703125 1.234375 -4.921875 1.328125 -5.109375 C 1.5 -5.46875 1.890625 -5.6875 2.375 -5.6875 C 3.0625 -5.6875 3.46875 -5.265625 3.46875 -4.578125 C 3.46875 -4.140625 3.3125 -3.859375 2.96875 -3.71875 C 2.765625 -3.625 2.484375 -3.59375 1.9375 -3.578125 Z M 1.9375 -2.921875 "/>
</symbol>
<symbol overflow="visible" id="glyph1-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph1-1">
<path style="stroke:none;" d="M 5.1875 -3.828125 C 5.140625 -4.390625 5.015625 -4.75 4.796875 -5.078125 C 4.40625 -5.609375 3.703125 -5.921875 2.90625 -5.921875 C 1.34375 -5.921875 0.34375 -4.703125 0.34375 -2.78125 C 0.34375 -0.921875 1.328125 0.25 2.890625 0.25 C 4.265625 0.25 5.140625 -0.578125 5.25 -1.984375 L 4.328125 -1.984375 C 4.171875 -1.0625 3.703125 -0.59375 2.921875 -0.59375 C 1.90625 -0.59375 1.296875 -1.421875 1.296875 -2.78125 C 1.296875 -4.21875 1.890625 -5.078125 2.890625 -5.078125 C 3.65625 -5.078125 4.140625 -4.625 4.25 -3.828125 Z M 5.1875 -3.828125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-2">
<path style="stroke:none;" d="M 2.796875 -5.765625 L 1.84375 -5.765625 L 1.84375 -7.34375 L 0.9375 -7.34375 L 0.9375 -5.765625 L 0.15625 -5.765625 L 0.15625 -5.015625 L 0.9375 -5.015625 L 0.9375 -0.65625 C 0.9375 -0.0625 1.328125 0.25 2.046875 0.25 C 2.28125 0.25 2.484375 0.234375 2.796875 0.171875 L 2.796875 -0.59375 C 2.65625 -0.5625 2.546875 -0.546875 2.359375 -0.546875 C 1.953125 -0.546875 1.84375 -0.65625 1.84375 -1.0625 L 1.84375 -5.015625 L 2.796875 -5.015625 Z M 2.796875 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-3">
<path style="stroke:none;" d="M 4.265625 -5.765625 L 2.671875 -1.28125 L 1.203125 -5.765625 L 0.21875 -5.765625 L 2.171875 0.015625 L 1.8125 0.9375 C 1.65625 1.34375 1.46875 1.5 1.078125 1.5 C 0.921875 1.5 0.796875 1.46875 0.59375 1.4375 L 0.59375 2.25 C 0.78125 2.359375 0.96875 2.390625 1.203125 2.390625 C 1.5 2.390625 1.828125 2.296875 2.0625 2.125 C 2.359375 1.90625 2.515625 1.671875 2.6875 1.203125 L 5.265625 -5.765625 Z M 4.265625 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-4">
<path style="stroke:none;" d="M 2.84375 -5.765625 L 1.875 -5.765625 L 1.875 -6.671875 C 1.875 -7.046875 2.09375 -7.25 2.515625 -7.25 C 2.59375 -7.25 2.625 -7.25 2.84375 -7.234375 L 2.84375 -8 C 2.625 -8.046875 2.515625 -8.046875 2.328125 -8.046875 C 1.46875 -8.046875 0.96875 -7.5625 0.96875 -6.75 L 0.96875 -5.765625 L 0.203125 -5.765625 L 0.203125 -5.015625 L 0.96875 -5.015625 L 0.96875 0 L 1.875 0 L 1.875 -5.015625 L 2.84375 -5.015625 Z M 2.84375 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-5">
<path style="stroke:none;" d="M 5.890625 -0.53125 C 5.78125 -0.515625 5.734375 -0.515625 5.6875 -0.515625 C 5.375 -0.515625 5.1875 -0.6875 5.1875 -0.96875 L 5.1875 -4.359375 C 5.1875 -5.375 4.4375 -5.921875 3.03125 -5.921875 C 2.171875 -5.921875 1.5 -5.6875 1.109375 -5.265625 C 0.84375 -4.96875 0.734375 -4.625 0.71875 -4.0625 L 1.640625 -4.0625 C 1.71875 -4.765625 2.140625 -5.078125 2.984375 -5.078125 C 3.828125 -5.078125 4.28125 -4.78125 4.28125 -4.21875 L 4.28125 -3.984375 C 4.265625 -3.59375 4.0625 -3.4375 3.328125 -3.34375 C 2.03125 -3.171875 1.828125 -3.140625 1.46875 -2.984375 C 0.796875 -2.703125 0.46875 -2.203125 0.46875 -1.453125 C 0.46875 -0.40625 1.1875 0.25 2.359375 0.25 C 3.078125 0.25 3.65625 0 4.3125 -0.59375 C 4.375 0 4.65625 0.25 5.265625 0.25 C 5.453125 0.25 5.578125 0.234375 5.890625 0.15625 Z M 4.28125 -1.8125 C 4.28125 -1.5 4.1875 -1.3125 3.921875 -1.0625 C 3.546875 -0.71875 3.09375 -0.546875 2.546875 -0.546875 C 1.84375 -0.546875 1.421875 -0.890625 1.421875 -1.46875 C 1.421875 -2.078125 1.8125 -2.390625 2.8125 -2.53125 C 3.78125 -2.65625 3.96875 -2.703125 4.28125 -2.84375 Z M 4.28125 -1.8125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-6">
<path style="stroke:none;" d="M 2.984375 -5.921875 C 1.359375 -5.921875 0.390625 -4.78125 0.390625 -2.84375 C 0.390625 -0.890625 1.359375 0.25 3 0.25 C 4.625 0.25 5.609375 -0.90625 5.609375 -2.796875 C 5.609375 -4.796875 4.65625 -5.921875 2.984375 -5.921875 Z M 3 -5.078125 C 4.03125 -5.078125 4.65625 -4.234375 4.65625 -2.8125 C 4.65625 -1.4375 4.015625 -0.59375 3 -0.59375 C 1.984375 -0.59375 1.359375 -1.4375 1.359375 -2.84375 C 1.359375 -4.234375 1.984375 -5.078125 3 -5.078125 Z M 3 -5.078125 "/>
</symbol>
<symbol overflow="visible" id="glyph1-7">
<path style="stroke:none;" d="M 0.765625 -5.765625 L 0.765625 0 L 1.6875 0 L 1.6875 -2.984375 C 1.6875 -4.375 2.265625 -5 3.53125 -4.96875 L 3.53125 -5.890625 C 3.375 -5.921875 3.28125 -5.921875 3.171875 -5.921875 C 2.578125 -5.921875 2.140625 -5.578125 1.609375 -4.71875 L 1.609375 -5.765625 Z M 0.765625 -5.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-8">
<path style="stroke:none;" d="M 2.59375 -8.015625 C 1.5 -6.578125 0.796875 -4.578125 0.796875 -2.84375 C 0.796875 -1.109375 1.5 0.890625 2.59375 2.328125 L 3.203125 2.328125 C 2.234375 0.765625 1.6875 -1.09375 1.6875 -2.84375 C 1.6875 -4.59375 2.234375 -6.453125 3.203125 -8.015625 Z M 2.59375 -8.015625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-9">
<path style="stroke:none;" d="M 1.671875 -8.015625 L 0.75 -8.015625 L 0.75 0 L 1.671875 0 Z M 1.671875 -8.015625 "/>
</symbol>
<symbol overflow="visible" id="glyph1-10">
<path style="stroke:none;" d="M 1.015625 2.328125 C 2.125 0.890625 2.8125 -1.109375 2.8125 -2.84375 C 2.8125 -4.578125 2.125 -6.578125 1.015625 -8.015625 L 0.421875 -8.015625 C 1.390625 -6.453125 1.921875 -4.59375 1.921875 -2.84375 C 1.921875 -1.09375 1.390625 0.765625 0.421875 2.328125 Z M 1.015625 2.328125 "/>
</symbol>
<symbol overflow="visible" id="glyph2-0">
<path style="stroke:none;" d=""/>
</symbol>
<symbol overflow="visible" id="glyph2-1">
<path style="stroke:none;" d="M -8.015625 -0.765625 L 0 -0.765625 L 0 -1.6875 L -3.171875 -1.6875 C -4.359375 -1.6875 -5.125 -2.296875 -5.125 -3.25 C -5.125 -3.546875 -5.03125 -3.84375 -4.875 -4.0625 C -4.671875 -4.328125 -4.40625 -4.4375 -4 -4.4375 L 0 -4.4375 L 0 -5.34375 L -4.359375 -5.34375 C -5.328125 -5.34375 -5.921875 -4.65625 -5.921875 -3.53125 C -5.921875 -2.71875 -5.671875 -2.21875 -4.96875 -1.6875 L -8.015625 -1.6875 Z M -8.015625 -0.765625 "/>
</symbol>
<symbol overflow="visible" id="glyph2-2">
<path style="stroke:none;" d="M 0 -6.09375 L -5.765625 -7.78125 L -5.765625 -6.75 L -1.28125 -5.609375 L -5.765625 -4.484375 L -5.765625 -3.359375 L -1.28125 -2.25 L -5.765625 -1.078125 L -5.765625 -0.0625 L 0 -1.734375 L 0 -2.765625 L -4.515625 -3.890625 L 0 -5.046875 Z M 0 -6.09375 "/>
</symbol>
<symbol overflow="visible" id="glyph2-3">
<path style="stroke:none;" d="M -5.765625 -4.265625 L -1.28125 -2.671875 L -5.765625 -1.203125 L -5.765625 -0.21875 L 0.015625 -2.171875 L 0.9375 -1.8125 C 1.34375 -1.65625 1.5 -1.46875 1.5 -1.078125 C 1.5 -0.921875 1.46875 -0.796875 1.4375 -0.59375 L 2.25 -0.59375 C 2.359375 -0.78125 2.390625 -0.96875 2.390625 -1.203125 C 2.390625 -1.5 2.296875 -1.828125 2.125 -2.0625 C 1.90625 -2.359375 1.671875 -2.515625 1.203125 -2.6875 L -5.765625 -5.265625 Z M -5.765625 -4.265625 "/>
</symbol>
</g>
<clipPath id="clip1">
  <path d="M 35.152344 23.246094 L 229.136719 23.246094 L 229.136719 234.925781 L 35.152344 234.925781 Z M 35.152344 23.246094 "/>
</clipPath>
<clipPath id="clip2">
  <path d="M 35.152344 203 L 229.136719 203 L 229.136719 205 L 35.152344 205 Z M 35.152344 203 "/>
</clipPath>
<clipPath id="clip3">
  <path d="M 35.152344 150 L 229.136719 150 L 229.136719 152 L 35.152344 152 Z M 35.152344 150 "/>
</clipPath>
<clipPath id="clip4">
  <path d="M 35.152344 97 L 229.136719 97 L 229.136719 98 L 35.152344 98 Z M 35.152344 97 "/>
</clipPath>
<clipPath id="clip5">
  <path d="M 35.152344 44 L 229.136719 44 L 229.136719 45 L 35.152344 45 Z M 35.152344 44 "/>
</clipPath>
<clipPath id="clip6">
  <path d="M 67 23.246094 L 68 23.246094 L 68 234.925781 L 67 234.925781 Z M 67 23.246094 "/>
</clipPath>
<clipPath id="clip7">
  <path d="M 101 23.246094 L 102 23.246094 L 102 234.925781 L 101 234.925781 Z M 101 23.246094 "/>
</clipPath>
<clipPath id="clip8">
  <path d="M 135 23.246094 L 136 23.246094 L 136 234.925781 L 135 234.925781 Z M 135 23.246094 "/>
</clipPath>
<clipPath id="clip9">
  <path d="M 169 23.246094 L 170 23.246094 L 170 234.925781 L 169 234.925781 Z M 169 23.246094 "/>
</clipPath>
<clipPath id="clip10">
  <path d="M 203 23.246094 L 204 23.246094 L 204 234.925781 L 203 234.925781 Z M 203 23.246094 "/>
</clipPath>
<clipPath id="clip11">
  <path d="M 35.152344 230 L 229.136719 230 L 229.136719 232 L 35.152344 232 Z M 35.152344 230 "/>
</clipPath>
<clipPath id="clip12">
  <path d="M 35.152344 177 L 229.136719 177 L 229.136719 179 L 35.152344 179 Z M 35.152344 177 "/>
</clipPath>
<clipPath id="clip13">
  <path d="M 35.152344 123 L 229.136719 123 L 229.136719 125 L 35.152344 125 Z M 35.152344 123 "/>
</clipPath>
<clipPath id="clip14">
  <path d="M 35.152344 70 L 229.136719 70 L 229.136719 72 L 35.152344 72 Z M 35.152344 70 "/>
</clipPath>
<clipPath id="clip15">
  <path d="M 50 23.246094 L 52 23.246094 L 52 234.925781 L 50 234.925781 Z M 50 23.246094 "/>
</clipPath>
<clipPath id="clip16">
  <path d="M 84 23.246094 L 86 23.246094 L 86 234.925781 L 84 234.925781 Z M 84 23.246094 "/>
</clipPath>
<clipPath id="clip17">
  <path d="M 118 23.246094 L 120 23.246094 L 120 234.925781 L 118 234.925781 Z M 118 23.246094 "/>
</clipPath>
<clipPath id="clip18">
  <path d="M 151 23.246094 L 154 23.246094 L 154 234.925781 L 151 234.925781 Z M 151 23.246094 "/>
</clipPath>
<clipPath id="clip19">
  <path d="M 185 23.246094 L 187 23.246094 L 187 234.925781 L 185 234.925781 Z M 185 23.246094 "/>
</clipPath>
<clipPath id="clip20">
  <path d="M 219 23.246094 L 221 23.246094 L 221 234.925781 L 219 234.925781 Z M 219 23.246094 "/>
</clipPath>
<clipPath id="clip21">
  <path d="M 35.152344 258.171875 L 229.136719 258.171875 L 229.136719 469.851562 L 35.152344 469.851562 Z M 35.152344 258.171875 "/>
</clipPath>
<clipPath id="clip22">
  <path d="M 35.152344 438 L 229.136719 438 L 229.136719 440 L 35.152344 440 Z M 35.152344 438 "/>
</clipPath>
<clipPath id="clip23">
  <path d="M 35.152344 385 L 229.136719 385 L 229.136719 387 L 35.152344 387 Z M 35.152344 385 "/>
</clipPath>
<clipPath id="clip24">
  <path d="M 35.152344 332 L 229.136719 332 L 229.136719 333 L 35.152344 333 Z M 35.152344 332 "/>
</clipPath>
<clipPath id="clip25">
  <path d="M 35.152344 278 L 229.136719 278 L 229.136719 280 L 35.152344 280 Z M 35.152344 278 "/>
</clipPath>
<clipPath id="clip26">
  <path d="M 67 258.171875 L 68 258.171875 L 68 469.851562 L 67 469.851562 Z M 67 258.171875 "/>
</clipPath>
<clipPath id="clip27">
  <path d="M 101 258.171875 L 102 258.171875 L 102 469.851562 L 101 469.851562 Z M 101 258.171875 "/>
</clipPath>
<clipPath id="clip28">
  <path d="M 135 258.171875 L 136 258.171875 L 136 469.851562 L 135 469.851562 Z M 135 258.171875 "/>
</clipPath>
<clipPath id="clip29">
  <path d="M 169 258.171875 L 170 258.171875 L 170 469.851562 L 169 469.851562 Z M 169 258.171875 "/>
</clipPath>
<clipPath id="clip30">
  <path d="M 203 258.171875 L 204 258.171875 L 204 469.851562 L 203 469.851562 Z M 203 258.171875 "/>
</clipPath>
<clipPath id="clip31">
  <path d="M 35.152344 465 L 229.136719 465 L 229.136719 467 L 35.152344 467 Z M 35.152344 465 "/>
</clipPath>
<clipPath id="clip32">
  <path d="M 35.152344 411 L 229.136719 411 L 229.136719 414 L 35.152344 414 Z M 35.152344 411 "/>
</clipPath>
<clipPath id="clip33">
  <path d="M 35.152344 358 L 229.136719 358 L 229.136719 360 L 35.152344 360 Z M 35.152344 358 "/>
</clipPath>
<clipPath id="clip34">
  <path d="M 35.152344 305 L 229.136719 305 L 229.136719 307 L 35.152344 307 Z M 35.152344 305 "/>
</clipPath>
<clipPath id="clip35">
  <path d="M 50 258.171875 L 52 258.171875 L 52 469.851562 L 50 469.851562 Z M 50 258.171875 "/>
</clipPath>
<clipPath id="clip36">
  <path d="M 84 258.171875 L 86 258.171875 L 86 469.851562 L 84 469.851562 Z M 84 258.171875 "/>
</clipPath>
<clipPath id="clip37">
  <path d="M 118 258.171875 L 120 258.171875 L 120 469.851562 L 118 469.851562 Z M 118 258.171875 "/>
</clipPath>
<clipPath id="clip38">
  <path d="M 151 258.171875 L 154 258.171875 L 154 469.851562 L 151 469.851562 Z M 151 258.171875 "/>
</clipPath>
<clipPath id="clip39">
  <path d="M 185 258.171875 L 187 258.171875 L 187 469.851562 L 185 469.851562 Z M 185 258.171875 "/>
</clipPath>
<clipPath id="clip40">
  <path d="M 219 258.171875 L 221 258.171875 L 221 469.851562 L 219 469.851562 Z M 219 258.171875 "/>
</clipPath>
<clipPath id="clip41">
  <path d="M 234.617188 23.246094 L 428.601562 23.246094 L 428.601562 234.925781 L 234.617188 234.925781 Z M 234.617188 23.246094 "/>
</clipPath>
<clipPath id="clip42">
  <path d="M 234.617188 203 L 428.601562 203 L 428.601562 205 L 234.617188 205 Z M 234.617188 203 "/>
</clipPath>
<clipPath id="clip43">
  <path d="M 234.617188 150 L 428.601562 150 L 428.601562 152 L 234.617188 152 Z M 234.617188 150 "/>
</clipPath>
<clipPath id="clip44">
  <path d="M 234.617188 97 L 428.601562 97 L 428.601562 98 L 234.617188 98 Z M 234.617188 97 "/>
</clipPath>
<clipPath id="clip45">
  <path d="M 234.617188 44 L 428.601562 44 L 428.601562 45 L 234.617188 45 Z M 234.617188 44 "/>
</clipPath>
<clipPath id="clip46">
  <path d="M 266 23.246094 L 268 23.246094 L 268 234.925781 L 266 234.925781 Z M 266 23.246094 "/>
</clipPath>
<clipPath id="clip47">
  <path d="M 300 23.246094 L 302 23.246094 L 302 234.925781 L 300 234.925781 Z M 300 23.246094 "/>
</clipPath>
<clipPath id="clip48">
  <path d="M 334 23.246094 L 336 23.246094 L 336 234.925781 L 334 234.925781 Z M 334 23.246094 "/>
</clipPath>
<clipPath id="clip49">
  <path d="M 368 23.246094 L 370 23.246094 L 370 234.925781 L 368 234.925781 Z M 368 23.246094 "/>
</clipPath>
<clipPath id="clip50">
  <path d="M 402 23.246094 L 404 23.246094 L 404 234.925781 L 402 234.925781 Z M 402 23.246094 "/>
</clipPath>
<clipPath id="clip51">
  <path d="M 234.617188 230 L 428.601562 230 L 428.601562 232 L 234.617188 232 Z M 234.617188 230 "/>
</clipPath>
<clipPath id="clip52">
  <path d="M 234.617188 177 L 428.601562 177 L 428.601562 179 L 234.617188 179 Z M 234.617188 177 "/>
</clipPath>
<clipPath id="clip53">
  <path d="M 234.617188 123 L 428.601562 123 L 428.601562 125 L 234.617188 125 Z M 234.617188 123 "/>
</clipPath>
<clipPath id="clip54">
  <path d="M 234.617188 70 L 428.601562 70 L 428.601562 72 L 234.617188 72 Z M 234.617188 70 "/>
</clipPath>
<clipPath id="clip55">
  <path d="M 249 23.246094 L 251 23.246094 L 251 234.925781 L 249 234.925781 Z M 249 23.246094 "/>
</clipPath>
<clipPath id="clip56">
  <path d="M 283 23.246094 L 285 23.246094 L 285 234.925781 L 283 234.925781 Z M 283 23.246094 "/>
</clipPath>
<clipPath id="clip57">
  <path d="M 317 23.246094 L 319 23.246094 L 319 234.925781 L 317 234.925781 Z M 317 23.246094 "/>
</clipPath>
<clipPath id="clip58">
  <path d="M 351 23.246094 L 353 23.246094 L 353 234.925781 L 351 234.925781 Z M 351 23.246094 "/>
</clipPath>
<clipPath id="clip59">
  <path d="M 385 23.246094 L 387 23.246094 L 387 234.925781 L 385 234.925781 Z M 385 23.246094 "/>
</clipPath>
<clipPath id="clip60">
  <path d="M 419 23.246094 L 421 23.246094 L 421 234.925781 L 419 234.925781 Z M 419 23.246094 "/>
</clipPath>
<clipPath id="clip61">
  <path d="M 234.617188 258.171875 L 428.601562 258.171875 L 428.601562 469.851562 L 234.617188 469.851562 Z M 234.617188 258.171875 "/>
</clipPath>
<clipPath id="clip62">
  <path d="M 234.617188 438 L 428.601562 438 L 428.601562 440 L 234.617188 440 Z M 234.617188 438 "/>
</clipPath>
<clipPath id="clip63">
  <path d="M 234.617188 385 L 428.601562 385 L 428.601562 387 L 234.617188 387 Z M 234.617188 385 "/>
</clipPath>
<clipPath id="clip64">
  <path d="M 234.617188 332 L 428.601562 332 L 428.601562 333 L 234.617188 333 Z M 234.617188 332 "/>
</clipPath>
<clipPath id="clip65">
  <path d="M 234.617188 278 L 428.601562 278 L 428.601562 280 L 234.617188 280 Z M 234.617188 278 "/>
</clipPath>
<clipPath id="clip66">
  <path d="M 266 258.171875 L 268 258.171875 L 268 469.851562 L 266 469.851562 Z M 266 258.171875 "/>
</clipPath>
<clipPath id="clip67">
  <path d="M 300 258.171875 L 302 258.171875 L 302 469.851562 L 300 469.851562 Z M 300 258.171875 "/>
</clipPath>
<clipPath id="clip68">
  <path d="M 334 258.171875 L 336 258.171875 L 336 469.851562 L 334 469.851562 Z M 334 258.171875 "/>
</clipPath>
<clipPath id="clip69">
  <path d="M 368 258.171875 L 370 258.171875 L 370 469.851562 L 368 469.851562 Z M 368 258.171875 "/>
</clipPath>
<clipPath id="clip70">
  <path d="M 402 258.171875 L 404 258.171875 L 404 469.851562 L 402 469.851562 Z M 402 258.171875 "/>
</clipPath>
<clipPath id="clip71">
  <path d="M 234.617188 465 L 428.601562 465 L 428.601562 467 L 234.617188 467 Z M 234.617188 465 "/>
</clipPath>
<clipPath id="clip72">
  <path d="M 234.617188 411 L 428.601562 411 L 428.601562 414 L 234.617188 414 Z M 234.617188 411 "/>
</clipPath>
<clipPath id="clip73">
  <path d="M 234.617188 358 L 428.601562 358 L 428.601562 360 L 234.617188 360 Z M 234.617188 358 "/>
</clipPath>
<clipPath id="clip74">
  <path d="M 234.617188 305 L 428.601562 305 L 428.601562 307 L 234.617188 307 Z M 234.617188 305 "/>
</clipPath>
<clipPath id="clip75">
  <path d="M 249 258.171875 L 251 258.171875 L 251 469.851562 L 249 469.851562 Z M 249 258.171875 "/>
</clipPath>
<clipPath id="clip76">
  <path d="M 283 258.171875 L 285 258.171875 L 285 469.851562 L 283 469.851562 Z M 283 258.171875 "/>
</clipPath>
<clipPath id="clip77">

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: draft.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="draft_files/md-default2.js" type="text/javascript"></script><script src="draft_files/md-default3.js" type="text/javascript"></script>

::: {.sourceClojure}
```clojure
(ns draft
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [representing]))
```
:::

# Draft explorations

::: {.sourceClojure}
```clojure
(-> "(ggplot(mpg, aes(cty, hwy)))"
    r
    representing/ggplot->clj
    (dissoc :data))
```
:::
